### 2016-01-31 article/main.tex

\documentclass[12pt,doc]{apa6}

\usepackage{blindtext}
\usepackage[american]{babel}
\usepackage[style=chicago,
            backend=biber,
            natbib=true,
            url=true]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{txfonts}
\usepackage{microtype}

\bibliography{main.bib}
\title{Ethical Academic Software Practices: the Case for Behavior-Driven
Development}
\author{David Kraemer}
\date{November 24, 2015}
\shorttitle{Behavior-Driven Development in Academia}
\affiliation{Grinnell College}
\leftheader{Kraemer}
\doublespacing

\begin{document}

    \maketitle

       \printbibliography

\end{document}

### 2016-01-31 scripts/FluidField.py
changes to FluidField.py

@@ -6,68 +6,64 @@ import matplotlib.pyplot as plt
 import matplotlib.animation as animation
 
 class FluidField:
-    
-    def __init__(self, tub, conv, F, rho, initial_temp):
-        
-        self.__tub = tub
-        self.__conv = conv
-        self.u = np.zeros((tub.rows,tub.columns,tub.intervals))
-        self.v = np.zeros((tub.rows,tub.columns,tub.intervals))
-        self.__p = np.ones((tub.rows,tub.columns,tub.intervals)) 
-        self.__b = np.zeros((tub.rows,tub.columns,tub.intervals))
-        self.__source_temperature = initial_temp
-        
-        # Field constants
-        
-        self.F = F
-        self.rho = rho
-    
-    def reinitialize(self):
-        self.u = np.zeros((tub.rows,tub.columns,tub.intervals))
-        self.v = np.zeros((tub.rows,tub.columns,tub.intervals))
-        self.__p = np.ones((tub.rows,tub.columns,tub.intervals)) 
-        self.__b = np.zeros((tub.rows,tub.columns,tub.intervals))
-        
-    def __buildUpB(self, source, rho, dt, dx, dy, u, v):
-        b = np.zeros_like(u)
-        
-        
-        
-        b[1:-1,1:-1]=rho*(1/dt*((u[1:-1,2:]-u[1:-1,0:-2])/(2*dx)+(v[2:,1:-1]-v[0:-2,1:-1])/(2*dy))-                          ((u[1:-1,2:]-u[1:-1,0:-2])/(2*dx))**2-                          2*((u[2:,1:-1]-u[0:-2,1:-1])/(2*dy)*(v[1:-1,2:]-v[1:-1,0:-2])/(2*dx))-                          ((v[2:,1:-1]-v[0:-2,1:-1])/(2*dy))**2)
-        return b
-    
-    def __presPoissPeriodic(self, p, dx, dy):
-        pn = np.empty_like(p)
-        
-        for q in range(nit):
-            pn = p.copy()
[…]

### 2016-01-31 scripts/FluidField.py
fixes

@@ -7,63 +7,76 @@ import matplotlib.animation as animation
 
 class FluidField:
 
-	def __init__(self, tub, conv, F, rho, initial_temp):
-		self.__tub = tub
-	self.__conv = conv
-	self.u = np.zeros((tub.rows,tub.columns,tub.intervals))
-	self.v = np.zeros((tub.rows,tub.columns,tub.intervals))
-	self.__p = np.ones((tub.rows,tub.columns,tub.intervals)) 
-	 self.__b = np.zeros((tub.rows,tub.columns,tub.intervals))
-	 self.__source_temperature = initial_temp
+    def __init__(self, tub, conv, F, rho, initial_temp):
+        self.__tub = tub
+        self.__conv = conv
+        self.u = np.zeros((tub.rows,tub.columns,tub.intervals))
+        self.v = np.zeros((tub.rows,tub.columns,tub.intervals))
+        self.__p = np.ones((tub.rows,tub.columns,tub.intervals)) 
+        self.__b = np.zeros((tub.rows,tub.columns,tub.intervals))
+        self.__source_temperature = initial_temp
 
-# Field constants
+        # Field constants
+        self.F = F
+        self.rho = rho
 
-	 self.F = F
-	 self.rho = rho
+    def reinitialize(self):
+        self.u = np.zeros((tub.rows,tub.columns,tub.intervals))
+        self.v = np.zeros((tub.rows,tub.columns,tub.intervals))
+        self.__p = np.ones((tub.rows,tub.columns,tub.intervals)) 
+        self.__b = np.zeros((tub.rows,tub.columns,tub.intervals))
 
-	 def reinitialize(self):
-	self.u = np.zeros((tub.rows,tub.columns,tub.intervals))
-	self.v = np.zeros((tub.rows,tub.columns,tub.intervals))
-	self.__p = np.ones((tub.rows,tub.columns,tub.intervals)) 
-	self.__b = np.zeros((tub.rows,tub.columns,tub.intervals))
+    def __buildUpB(self, source, rho, dt, dx, dy, u, v):
[…]

### 2016-01-31 scripts/Bathtub.py
Renaming some stuff

@@ -1,0 +1,44 @@
+# As of January 31 2016 (12:30 AM)
+# TODO: make changes to work with Logan's code
+#       add static plots and visualization
+#       incorporate with fluid simulation
+
+import numpy as np 
+import matplotlib.pyplot as plt 
+import matplotlib.animation as animation
+
+class Bathtub:
+    """
+    Bathtub class, for specifying the geometry and other parameters
+    needed to perform diffusion.
+
+    Every parameter is public and accessible. This class is just a way to
+    organize the information for the Diffuser class.
+    """
+
+    def __init__(self, box_shape, box_dims, intervals=100, duration=60,
+            temp=0.0, alpha=1e-7, material=1.0):
+        """
+        Bathtub class initialization method.
+
+        Arguments:
+        box_shape -- a 2-element list of integers specifying rows and cols
+        box_dims -- a 2-element list of floats specifying length and width
+
+
+        Keyword arguments:
+        intervals -- number of time steps for the diffusion (default 100)
+        duration -- number of time units for the diffusion (default 60)
+        temp -- global temperature default (default 0.0)
+        alpha -- diffusion parameter (default 1e-7)
+        """
+
+        self.rows = box_shape[0]
+        self.cols = box_shape[1]
+        self.length = box_dims[0]
+        self.width = box_dims[1]
+        self.intervals = intervals
+        self.duration = duration
+        self.temp = temp
+        self.alpha = alpha
+        self.material = 1.0

### 2016-01-31 scripts/Convector.py

@@ -1,0 +1,187 @@
+# As of January 31 2016 (12:30 AM)
+# TODO: make changes to work with Logan's code
+#       add static plots and visualization
+#       incorporate with fluid simulation
+# This is a test
+
+import numpy as np 
+import matplotlib.pyplot as plt 
+import matplotlib.animation as animation
+
+class Diffuser:
+    """
+    A class for running simulated heat diffusion by numerically solving the
+    partial differential equation
+    \[
+    \frac{\partial u}{\partial t} - \alpha \nabla^2 u,
+    \]
+    where $u : \Omega \times \mathbb{R} \to \mathbb{R}$ is a temperature 
+    function and $\Omega \subseteq \mathbb{R}^2$.
+    """
+    def __init__(self, tub, source=False, fig=plt.figure()):
+        """
+        Diffuser class initialization method.
+
+        Arguments:
+        tub -- a Bathtub object
+        source -- indicates whether a heat source is present (default False)
+        fig -- where to send plots (default plt.figure())
+        """
+        self.__tub = tub
+        self.__dx = self.__tub.length / self.__tub.cols
+        self.__dy = self.__tub.width / self.__tub.rows
+        self.__dt = self.__tub.duration / self.__tub.intervals
+        self.grid = np.ones((self.__tub.rows + 1, self.__tub.cols + 1,
+                             self.__tub.intervals))  * self.__tub.temp
+        self.__source = source
+        self.__ellipse = (0,0,0,0)
+        self.__fig = fig
+
+    def get_dx():
+        return self.__dx
+
+    def get_dy():
+        return self.__dy
+
+    def get_dt():
+        return self.__dt
+
+
+    def stable(self):
+        """
+        Method to determine if current tub will produce numerically stable
+        results. It verifies the following inequality:
+        \[
+        dt \leq \frac{1}{2\alpha} \frac{(dx \ dy)^2}{(dx)^2 + (dy)^2)}
+        \]
+        Source: pending
+        """
+        dx, dy, dt = [self.__dx, self.__dy, self.__dt]
+        alpha = self.__tub.alpha
+        return (dt <= 1.0/(2.0 * alpha) * (dx * dy)**2 / (dx**2 + dy**2))
+
+    def define_boundary(self):
+        pass
+
+    def ij_to_xy(self, i, j):
+        """
+        Converts a grid (i,j) row-column coordinate on the meshgrid into a
[…]

### 2016-01-31 scripts/Convector.py
Renaming some stuff

@@ -8,7 +8,7 @@ import numpy as np
 import matplotlib.pyplot as plt 
 import matplotlib.animation as animation
 
-class Diffuser:
+class Convector:
     """
     A class for running simulated heat diffusion by numerically solving the
     partial differential equation
@@ -20,7 +20,7 @@ class Diffuser:
     """
     def __init__(self, tub, source=False, fig=plt.figure()):
         """
-        Diffuser class initialization method.
+        Convector class initialization method.
 
         Arguments:
         tub -- a Bathtub object
@@ -133,38 +133,38 @@ class Diffuser:
 
     def diffusion_step(self, t):
         r"""
-Computes the next iteration of diffusion across the grid, using
-the update step
-\[
-T_{i,j,t+1} = T_{i,j,t} + \alpha \Nabla^2 T_{i,j,t},
-\]
-where 
-\[
-\Nabla^2 T = \frac{\partial^2 T}{\partial x^2} + 
-\frac{\partial^2 T}{\partial y^2}
-\]
-is the 2D Laplacian.
-
-Arguments:
-t -- the current time index (int)
-""" 
-
-m = self.__tub.rows
-n = self.__tub.cols
-dx = self.__dx
-dy = self.__dy
-dt = self.__dt
-alpha = self.__tub.alpha
-
-for i in range(1, m):
-    for j in range(1, n):
-        # Compute numerical approximation of the Laplacian
-        xlap = Diffuser.central_second_diff(self.grid[i,j+1,t], 
-                                            self.grid[i,j,t], self.grid[i,j-1,t], dx)
-        ylap = Diffuser.central_second_diff(self.grid[i-1,j,t], 
-                                            self.grid[i,j,t], self.grid[i+1,j,t], dy)
-        if not (self.__source and self.calculate_ellipse(i, j)):
-            self.grid[i,j,t+1] = self.grid[i,j,t] + alpha  * (xlap + ylap) * dt
+        Computes the next iteration of diffusion across the grid, using
+        the update step
+        \[
+        T_{i,j,t+1} = T_{i,j,t} + \alpha \Nabla^2 T_{i,j,t},
+        \]
+        where 
+        \[
+        \Nabla^2 T = \frac{\partial^2 T}{\partial x^2} + 
+        \frac{\partial^2 T}{\partial y^2}
+        \]
+        is the 2D Laplacian.
+        
+        Arguments:
+        t -- the current time index (int)
+        """ 
+        
[…]

### 2016-01-31 scripts/Convector.py
The Convector.py is now actually a convection process!

@@ -18,7 +18,7 @@ class Convector:
     where $u : \Omega \times \mathbb{R} \to \mathbb{R}$ is a temperature 
     function and $\Omega \subseteq \mathbb{R}^2$.
     """
-    def __init__(self, tub, source=False, fig=plt.figure()):
+    def __init__(self, tub, vfield, source=False, fig=plt.figure()):
         """
         Convector class initialization method.
 
@@ -28,6 +28,7 @@ class Convector:
         fig -- where to send plots (default plt.figure())
         """
         self.__tub = tub
+        self.__vfield = vfield
         self.__dx = self.__tub.length / self.__tub.cols
         self.__dy = self.__tub.width / self.__tub.rows
         self.__dt = self.__tub.duration / self.__tub.intervals
@@ -126,12 +127,12 @@ class Convector:
         return num / den
 
     def forward_diff(next_u, current_u, delta):
-        pass
+        return (next_u - current_u) / delta
 
     def backward_diff(current_u, prev_u, delta):
         return forward_diff(current_u, prev_u, delta)
 
-    def diffusion_step(self, t):
+    def convection_step(self, t):
         r"""
         Computes the next iteration of diffusion across the grid, using
         the update step
@@ -156,15 +157,24 @@ class Convector:
         dt = self.__dt
         alpha = self.__tub.alpha
         
-        for i in range(1, m):
-            for j in range(1, n):
+        for i in range(1, m-1):
+            for j in range(1, n-1):
+                # Computes the gradient
+                xgrad = Convector.forward_diff(self.grid[i,j+1,t],
+                                               self.grid[i,j,t], dx)
+                ygrad = Convector.forward_diff(self.grid[i-1,j,t],
+                                               self.grid[i,j,t], dy)
                 # Compute numerical approximation of the Laplacian
                 xlap = Convector.central_second_diff(self.grid[i,j+1,t], 
                                                     self.grid[i,j,t], self.grid[i,j-1,t], dx)
                 ylap = Convector.central_second_diff(self.grid[i-1,j,t], 
                                                     self.grid[i,j,t], self.grid[i+1,j,t], dy)
+
+                update = alpha * (xlap + ylap) - (xgrad * vfield.u[i,j,t] +
+                                                  ygrad * vfield.v[i,j,t])
+
                 if not (self.__source and self.calculate_ellipse(i, j)):
[…]

### 2016-02-01 scripts/Convector.py
Merging changes to FluidFlow

@@ -18,7 +18,7 @@ class Convector:
     where $u : \Omega \times \mathbb{R} \to \mathbb{R}$ is a temperature 
     function and $\Omega \subseteq \mathbb{R}^2$.
     """
-    def __init__(self, tub, vfield, source=False, fig=plt.figure()):
+    def __init__(self, tub, source=False, fig=plt.figure()):
         """
         Convector class initialization method.
 
@@ -28,7 +28,6 @@ class Convector:
         fig -- where to send plots (default plt.figure())
         """
         self.__tub = tub
-        self.__vfield = vfield
         self.__dx = self.__tub.length / self.__tub.cols
         self.__dy = self.__tub.width / self.__tub.rows
         self.__dt = self.__tub.duration / self.__tub.intervals
@@ -46,6 +45,9 @@ class Convector:
 
     def get_dt():
         return self.__dt
+    
+    def set_vfield(vfield):
+        self.__vfield = vfield
 
 
     def stable(self):

### 2016-02-01 scripts/Convector.py
Updated convector

@@ -35,7 +35,8 @@ class Convector:
         self.grid = np.ones((self.__tub.rows + 1, self.__tub.cols + 1,
                              self.__tub.intervals))  * self.__tub.temp
         self.__source = source
-        self.__ellipse = (0,0,0,0)
+        self.__source_ellipsoid = (0,0,0,0,0)
+        self.__boundary_ellipsoid = (0,0,0,0,0)
         self.__fig = fig
 
     def get_dx():
@@ -61,8 +62,8 @@ class Convector:
         alpha = self.__tub.alpha
         return (dt <= 1.0/(2.0 * alpha) * (dx * dy)**2 / (dx**2 + dy**2))
 
-    def define_boundary(self):
-        pass
+    def define_boundary(self, ellipsoid):
+        self.__boundary_ellipsoid = ellipsoid
 
     def ij_to_xy(self, i, j):
         """
@@ -72,19 +73,25 @@ class Convector:
         return ((j/self.__tub.cols - 1/2)*self.__tub.length, (1/2 - \
                                                               i/self.__tub.rows)*self.__tub.width)
 
-    def calculate_ellipse(self, i, j):
+    def check_ellipsoid(self, i, j, ellipsoid):
         x, y = self.ij_to_xy(i, j)
-        h, k, a, b = self.__ellipse
-        return np.power((x - h) / a, 2.0) + np.power((y - k) / b, 2.0) <= 1.0
+        h, k, a, b, p = ellipsoid
+        return np.power((x - h) / a, p) + np.power((y - k) / b, p) <= 1.0
+
+    def calculate_ellipsoid(self, i, j):
+        return check_ellipsoid(self, i, j, self.__source_ellipsoid)
+
+    def mask_ellipsoid(self, i, j):
+        return check_ellipsoid(self, i, j, self.__boundary_ellipsoid)
 
 
-    def setup_source(self, ellipse, temperature, source=False):
+    def setup_source(self, ellipsoid, temperature, source=False):
         """ 
         Add a \"faucet\" source to the first iteration of the diffusion 
         simulation. If the argument source is True, make this source permanent.
 
         Arguments:
-        ellipse -- a list of 4 floats [h,k,a,b] which will define the inequality
+        ellipsoid -- a list of 4 floats [h,k,a,b] which will define the inequality
         \[
         (x  - h)^2 / a^2 + (y - k)^2 / b^2 <= 1,
         \]
@@ -96,14 +103,14 @@ class Convector:
[…]

### 2016-02-01 scripts/Convector.py
It's crunch time

@@ -38,16 +38,16 @@ class Convector:
         self.__boundary_ellipsoid = (0,0,0,0,0)
         self.__fig = fig
 
-    def get_dx():
+    def get_dx(self):
         return self.__dx
 
-    def get_dy():
+    def get_dy(self):
         return self.__dy
 
-    def get_dt():
+    def get_dt(self):
         return self.__dt
     
-    def set_vfield(vfield):
+    def set_vfield(self, vfield):
         self.__vfield = vfield
 
 
@@ -81,10 +81,10 @@ class Convector:
         return np.power((x - h) / a, p) + np.power((y - k) / b, p) <= 1.0
 
     def calculate_ellipsoid(self, i, j):
-        return check_ellipsoid(self, i, j, self.__source_ellipsoid)
+        return self.check_ellipsoid(i, j, self.__source_ellipsoid)
 
     def mask_ellipsoid(self, i, j):
-        return check_ellipsoid(self, i, j, self.__boundary_ellipsoid)
+        return self.check_ellipsoid(i, j, self.__boundary_ellipsoid)
 
 
     def setup_source(self, ellipsoid, temperature, source=False):
@@ -165,6 +165,8 @@ class Convector:
         dy = self.__dy
         dt = self.__dt
         alpha = self.__tub.alpha
+        u = self.__vfield.get_u()
+        v = self.__vfield.get_v()
         
         for i in range(m):
             for j in range(n):
@@ -180,8 +182,8 @@ class Convector:
                     ylap = Convector.central_second_diff(self.grid[i-1,j,t], 
                                                         self.grid[i,j,t], self.grid[i+1,j,t], dy)
 
-                    update = alpha * (xlap + ylap) - (xgrad * vfield.u[i,j,t] +
-                                                      ygrad * vfield.v[i,j,t])
+                    update = alpha * (xlap + ylap) - (xgrad * u[i,j,t] +
+                                                      ygrad * v[i,j,t])
 
                     if not (self.__source and self.calculate_ellipsoid(i, j)):
                         self.grid[i,j,t+1] = self.grid[i,j,t] + update * dt
@@ -197,7 +199,8 @@ class Convector:
         """
         ims = []
         for t in range(self.__tub.intervals-1):
-            self.diffusion_step(t)
+            self.convection_step(t)
+            self.__vfield.fluid_field(self.__source_ellipsoid, None, t)
             im = plt.imshow(self.grid[:,:,t], **kwargs)
             ims.append([im])
         plt.colorbar()

### 2016-02-01 scripts/FluidField.py

@@ -5,6 +5,15 @@ import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib.animation as animation
 
+def forward_diff(future, current, delta):
+    return (future - current) / delta
+
+def backward_diff(current, past, delta):
+    return (current - past) / delta
+
+def second_diff(future, current, past, delta):
+    return (future - 2 * current + past) / (delta * delta)
+
 class FluidField:
 
     def __init__(self, tub, F, rho, initial_temp):
@@ -14,13 +23,14 @@ class FluidField:
         self.__p = np.ones((tub.rows,tub.cols,tub.intervals)) 
         self.__b = np.zeros((tub.rows,tub.cols,tub.intervals))
         self.__source_temperature = initial_temp
-
+        
         # Field constants
         self.__F = F
         self.__rho = rho
 
-    def get_u(): return u
-    def get_v(): return v
+    def get_u(self): return self.__u
+    def get_v(self): return self.__v
+    def get_p(self): return self.__p
         
     def set_conv(self, conv):
         self.__conv = conv
@@ -31,86 +41,70 @@ class FluidField:
         self.__p = np.ones((tub.rows,tub.cols,tub.intervals)) 
         self.__b = np.zeros((tub.rows,tub.cols,tub.intervals))
 
-    def buildUpB(self, rho, dt, dx, dy, u, v, t, ellipse):
-        self.__b = np.zeros_like(u)
-        axis1, axis2, q = ellipse
-        
-        print(u[0,0,0])
-        
-        for i in range(1, np.shape(u)[0]):
-            for j in range(1, np.shape(v)[1]):
-                if np.power(i / axis1, q) + np.power(j / axis2, q) <= 1:
-                    self.__b[i,j,t] = rho * (1 / dt * ((u[i,j+1,t-1] - u[i,j-1,t-1]) / (2 * dx) + \
-                            (v[i+1,j,t-1] - v[i-1,j,t-1]) / (2 * dy)) - \
-                            np.power((u[i,j+1,t-1] - u[i,j-1,t-1]) / (2 * dx), 2.0) - 2 * \
-                            (u[i+1,j,t-1] - u[i-1,j,t-1]) / (2 * dy) * \
-                            (v[i,j+1,t-1] - v[i,j-1,t-1]) / (2 * dx) - \
[…]

### 2016-02-01 scripts/simple_script.py

@@ -1,0 +1,52 @@
+from Convector import Convector
+from FluidField import FluidField
+from Bathtub import Bathtub
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+rows = 2**5
+cols = 2**5
+
+length = 1.0
+width = 1.0
+
+intervals = 200
+duration = 60
+
+temperature = 20.0
+initial_temp = 10.0
+alpha = 1e-4
+material = 1.0
+F = 0.0
+rho = 1.0
+
+tub = Bathtub([rows, cols], [length,width], intervals, duration, temperature,
+alpha, material)
+
+heat = Convector(tub)
+vfield = FluidField(tub, F, rho, initial_temp)
+
+heat.set_vfield(vfield)
+vfield.set_conv(heat)
+
+boundary = (0,0,length,width, 3.0)
+heat.define_boundary(boundary)
+
+source = (-0.5, 0, 0.2, 0.2, 2.0)
+heat.setup_source(source, temperature + 50.0, source=True)
+vfield.setup_b(source, 25.0, 0)
+vfield.compute_pressure(0)
+
+print(heat.stable())
+
+# for t in range(1,10):
+#     vfield.fluid_field(source, None, t)
+#     heat.convection_step(t)
+#     plt.imshow(heat.grid[:,:,t])
+#     plt.show()
+#     plt.close()
+# 
+# 
+# 
+heat.animate(cmap="gray",vmin=0.0,vmax=80,interpolation="nearest")

### 2016-02-01 article/main.tex
article drafting

@@
-\documentclass[12pt,doc]{apa6}
+\documentclass[12pt]{article}
 
 \usepackage{blindtext}
+\usepackage[utf8]{inputenc}
 \usepackage[american]{babel}
-\usepackage[style=chicago,
+
+\usepackage{csquotes}
+\usepackage[style=numeric,
+    citestyle=numeric,
     backend=biber,
@@
 url=true]{biblatex}
-\DeclareLanguageMapping{american}{american-apa}
+
 \usepackage[hidelinks]{hyperref}
 \usepackage{setspace}
-\usepackage{txfonts}
 \usepackage{microtype}
@@
 \bibliography{main.bib}
-\title{Ethical Academic Software Practices: the Case for Behavior-Driven
-Development}
-\author{David Kraemer}
-\date{November 24, 2015}
-\shorttitle{Behavior-Driven Development in Academia}
-\affiliation{Grinnell College}
-\leftheader{Kraemer}
-\doublespacing
+
+\usepackage[margin=1in]{geometry}
+
+\usepackage{amsmath, amssymb, amsthm}
+
+% Custom macros
+\newcommand{\la}{\overleftarrow}
+\newcommand{\ra}{\overrightarrow}
+\newcommand{\ca}{\overleftrightarrow}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\abs}[1]{\left|#1\right|}
+\DeclareMathOperator*{\argmin}{\mathrm{arg\,min}}
+
+\title{Numerical simulation of two-dimensional heat convection-diffusion with
+ellipsoid geometries}
+
+\date{February 1, 2016}
 
@@
 
+\begin{abstract}
+    This is a test.
+\end{abstract}
+
+\section{Introduction}
+
+\section{Model overview}
+
+Throughout this work we will denote the spatial region under scrutiny by
+$\Omega \subseteq \R^2$, and we write $\partial \Omega$ to indicate the
+boundary of the region. The function $T : \Omega \times \R_{\geq 0} \to \R$
+will denote the temperature $T = T(x,y,t)$, and the functions $v_x : \Omega
+\times \R_{\geq 0} \to \R$ and $v_y : \Omega \times \R_{\geq 0} \to \R$ will
+denote $v_x = v_x(x,y,t)$ the horizontal and $v_y = v_y(x,y,t)$ the vertical
+components of the velocity of the fluid flow.
+
+\subsection{Two-dimensional Navier-Stokes formulation}
+
+The Navier-Stokes equations for an incompressible fluid are given by
+\begin{align}
+    \nabla \cdot v &= 0 \\
+    \frac{\partial v}{\partial t} + (v \cdot \nabla) v &= -
+    \frac{1}{\rho} \nabla p + \alpha \nabla^2 v
+    \label{eq:\theequation}
+\end{align}
+where $v = (v_x, v_y)$ is the fluid velocity, $\rho$ denotes mass density of
+the fluid, and $p$ denotes pressure. Incompressibility is incorporated
+through Equation (), since nonzero divergence implies the presence of either
+sources or sinks of fluid. Now because $v$ is two-dimensional, Equation
+() actually implies a pair of partial differential equations for both the $x$
+and $y$ components. The pressure $p$ is determined through the Poisson equation
+\begin{equation}
+    \nabla^2 p = b,
+    \label{eq:\theequation}
+\end{equation}
+where $b$ is taken as a constant term for the purposes of this study. Many
+wonderful resources exist online for understanding the formulation of these
+equations, specifically Barba's work \cite{12-steps}, but we do not include a
+derivation of these relations here.
+
+\subsection{Heat convection-diffusion equation}
+
+The heat convection-diffusion equation found in the literature
+\cite{convection-diffusion},
+\begin{equation}
+    \frac{\partial T}{\partial t} - \alpha \nabla^2 T + v \cdot \nabla T =
+    0,
+    \label{eq:\theequation}
+\end{equation}
+is a combination of parabolic and hyperbolic partial differential equations
+relating the temporal change in temperature with its spatial diffusion and
+the flow of heat packets elsewhere in the fluid.     Here, $\nabla$ is the
+gradient operator $\left( \frac{\partial}{\partial x},
+\frac{\partial}{\partial y} \right)$, $\nabla^2$ denotes the Laplacian
+$\frac{\partial^2}{\partial x^2} + \frac{\partial^2}{\partial y^2}$, $v =
+(v_x, v_y)$ denotes the fluid velocity vector, and $\alpha$ is a diffusivity
+constant.
+
+The ubiquity of parabolic PDEs in modeling scientific phenomenon is well
+known, since it captures the essence of diffusive processes. Elliptic PDEs
+often arise out of physical environments with a present potential field
+(e.g.  gravitational or electrostatic), or in the cases of incompressible
+fluid flow \cite{convection-diffusion, ames}. We use the latter for
+motivating this model, as bathtub water exhibits the standard
+characteristics of incompressible fluid.
+
+\subsection{Numerical methods}
+
+We proceed by providing a brief overview of the numerical methods used in
+this study. To approximate the solution to a PDE, we discretize the region
+$\Omega$ under consideration into a coordinate mesh. For convention, we
+write $T_{i,j}^{n}$ to denote the temperature at the $(i,j)$ mesh coordinate
+at the time interval $t=n$.
+
+Modifying the notation employed by Ames \cite{ames}, we establish the
+following nomenclature for the numerical operations in the model:
+
+\begin{center}
+    \begin{tabular}[]{ll}
+        $\ra{\Delta_i} T_{i,j}^n = T_{i+1,j}^n - T_{i,j}^n$ & Forward
+        differencing \\
+        $\la{\Delta_i} T_{i,j}^n = T_{i,j}^n - T_{i-1,j}^n$ & Backward differencing \\
+        $\ca{\Delta_i} T_{i,j}^n = T_{i+1/2,j}^n - T_{i-1/2,j}^n$ & Central differencing
+    \end{tabular}
+\end{center}
+
+For
+
+\subsection{Bathtub optimization problem}
+
+The goal of this study is to identify a process through which the avid bather
+may seek to achieve uniform water temperature, ideally wasting as little water
+as possible. Using the aforementioned numerical models to simulate bathtub
+dynamics, we propose an optimization problem by which to approach this goal. Let
+$t_{\mathrm{total}}$ indicate the period in which the faucet is turned on, let
+$T_{\mathrm{f}}$ denote the temperature of the water in the faucet, and let
+$V(t)$ denote the total volume of water that has left the faucet. We assume that
+$\frac{dV}{dt} = c$, i.e., the strength of the faucet is fixed at a chosen $c$ throughout the
+duration of the bath. Now, consider the surface integral
+\begin{equation}
+    f_{\mathrm{cont}}(t) = \int_{\Omega} \abs{T(x,y,t) - T_{\mathrm{f}}} \ d\omega.
+    \label{eq:\theequation}
+\end{equation}
+We propose the minimization problem
+\begin{equation}
+    \argmin_{c} V(t_{\mathrm{total}}) \quad \text{such that} \quad \int_{0}^{t_{\mathrm{total}}}
+    f_{\mathrm{cont}}(t) \ dt < \gamma,
+    \label{eq:\theequation}
+\end{equation}
+where $\gamma$ is some tolerance for variation. This is minimization
+problem is subject to a total variation constraint, which has been subject to
+considerable study, especially within the context of medical imaging
+\cite{Zhang2005}.
+
+This optimization leads to a natural discretization. We rewrite:
+\begin{align}
+    V(t) &\longrightarrow V^t \\
+    \frac{dV}{dt} = c &\longrightarrow V^{t+1} - V^t = c \\
+    f_{\mathrm{cont}}(t) = \int_{\Omega} \abs{T(x,y,t) - T_{\mathrm{f}}} \
+    d\omega &\longrightarrow f_{\mathrm{disc}}(t) = \sum_{x,y}\abs{T(x,y,t) -
+        T_{\mathrm{f}}},
+\end{align}
+which translate to the problem
+\begin{equation}
+    \argmin_{c} V^{t_{\mathrm{total}}} \quad \text{such that} \quad
+    \sum_{t=0}^{t_{\mathrm{total}}} f_{\mathrm{disc}}(t) < \gamma.
+    \label{eq:\theequation}
+\end{equation}
+
+\section{Empirical results}
+
+\section{Analysis}
+
+\section{Discussion}
+
+\nocite{air}
+
 \printbibliography

### 2016-02-01 scripts/FluidField.py
debugging fluidflow

@@ -16,13 +16,14 @@ def second_diff(future, current, past, delta):
 
 class FluidField:
 
-    def __init__(self, tub, F, rho, initial_temp):
+    def __init__(self, tub, F, rho, initial_temp, initial_b):
         self.__tub = tub
         self.__u = np.zeros((tub.rows,tub.cols,tub.intervals))
         self.__v = np.zeros((tub.rows,tub.cols,tub.intervals))
         self.__p = np.ones((tub.rows,tub.cols,tub.intervals)) 
         self.__b = np.zeros((tub.rows,tub.cols,tub.intervals))
         self.__source_temperature = initial_temp
+        self.__initial_b = initial_b
         
         # Field constants
         self.__F = F
@@ -42,11 +43,11 @@ class FluidField:
         self.__b = np.zeros((tub.rows,tub.cols,tub.intervals))
 
     def setup_b(self, ellipsoid, initial_b, t):
-        h, k, a, b, p = ellipsoid
         for i in range(self.__tub.rows):
-            for j in range(self.__tub.cols):              
+            for j in range(self.__tub.cols):
                 if self.__conv.check_ellipsoid(i, j, ellipsoid):
-                    self.__b[i,j,t] = initial_b
+                    print(initial_b*(i-j+4))
+                    self.__b[i,j,t] = initial_b*np.abs(i-j+4)
                 else:
                     self.__b[i,j,t] = 0.0
 
@@ -58,11 +59,17 @@ class FluidField:
         p = self.__p
         for i in range(1, self.__tub.rows - 1):
             for j in range(1, self.__tub.cols - 1):
+                print("b. ", self.__b[i,j,t])
                 result = (p[i+1,j, t-1] + p[i-1, j, t-1]) * dy
+                print("1. ",result)
                 result += (p[i, j+1, t-1] + p[i, j-1, t-1]) * dx
-                result -= self.__b[i,j,t-1] * dx * dy
+                print("2. ",result)
+                result -= self.__b[i,j,t] * dx * dy
+                print("3. ",result)
                 result /= (2 * (dx + dy))
-                self.__p[i, j, t] = result 
+                print("4. ",result)
+                self.__p[i, j, t] = result
+                
                 
 
     def fluid_field(self, source_ellipsoid, sink_ellipsoid, t):
@@ -75,25 +82,25 @@ class FluidField:
         b = self.__b
         dx = self.__conv.get_dx()
         dy = self.__conv.get_dy()
-        dt = self.__conv.get_dt() 
[…]

### 2016-02-01 scripts/old-bathtub.py

@@ -17,7 +17,7 @@ class Bathtub:
     """
 
     def __init__(self, box_shape, box_dims, intervals=100, duration=60,
-            temp=0.0, alpha=1e-7, material=1.0):
+            temp=0.0, alpha=1e-7, ellipse=(0,0,0)):
         """
         Bathtub class initialization method.
 
@@ -27,11 +27,11 @@ class Bathtub:
 
 
         Keyword arguments:
-        intervals -- number of time steps for the convection (default 100)
-        duration -- number of time units for the convection (default 60)
+        intervals -- number of time steps for the diffusion (default 100)
+        duration -- number of time units for the diffusion (default 60)
         temp -- global temperature default (default 0.0)
         alpha -- diffusion parameter (default 1e-7)
-        material -- represents bathtub material (default 1.0)
+        ellipse -- ordered triple containing the major and minor axes. 
         """
 
         self.rows = box_shape[0]
@@ -42,4 +42,5 @@ class Bathtub:
         self.duration = duration
         self.temp = temp
         self.alpha = alpha
-        self.material = 1.0
+        self.tubshape = ellipse
+

### 2016-02-01 scripts/old-diffuser.py

@@ -8,19 +8,19 @@ import numpy as np
 import matplotlib.pyplot as plt 
 import matplotlib.animation as animation
 
-class Convector:
+class Diffuser:
     """
     A class for running simulated heat diffusion by numerically solving the
     partial differential equation
     \[
-    \frac{\partial u}{\partial t} - \alpha \nabla^2 u,
+        \frac{\partial u}{\partial t} - \alpha \nabla^2 u,
     \]
     where $u : \Omega \times \mathbb{R} \to \mathbb{R}$ is a temperature 
     function and $\Omega \subseteq \mathbb{R}^2$.
     """
     def __init__(self, tub, source=False, fig=plt.figure()):
         """
-        Convector class initialization method.
+        Diffuser class initialization method.
 
         Arguments:
         tub -- a Bathtub object
@@ -32,23 +32,20 @@ class Convector:
         self.__dy = self.__tub.width / self.__tub.rows
         self.__dt = self.__tub.duration / self.__tub.intervals
         self.grid = np.ones((self.__tub.rows + 1, self.__tub.cols + 1,
-                             self.__tub.intervals))  * self.__tub.temp
+            self.__tub.intervals)) \
+                    * self.__tub.temp
         self.__source = source
-        self.__source_ellipsoid = (0,0,0,0,0)
-        self.__boundary_ellipsoid = (0,0,0,0,0)
+        self.__ellipse = (0,0,0,0)
         self.__fig = fig
 
-    def get_dx(self):
-        return self.__dx
+	def get_dx():
+		return self.__dx
 
-    def get_dy(self):
-        return self.__dy
+	def get_dy():
+		return self.__dy
 
-    def get_dt(self):
-        return self.__dt
-    
-    def set_vfield(self, vfield):
-        self.__vfield = vfield
+	def get_dt():
+		return self.__dt
 
 
     def stable(self):
@@ -56,7 +53,7 @@ class Convector:
         Method to determine if current tub will produce numerically stable
         results. It verifies the following inequality:
         \[
-        dt \leq \frac{1}{2\alpha} \frac{(dx \ dy)^2}{(dx)^2 + (dy)^2)}
+            dt \leq \frac{1}{2\alpha} \frac{(dx \ dy)^2}{(dx)^2 + (dy)^2)}
         \]
         Source: pending
         """
@@ -64,38 +61,32 @@ class Convector:
         alpha = self.__tub.alpha
[…]

### 2016-02-01 scripts/simple_script.py

@@ -5,8 +5,8 @@ from Bathtub import Bathtub
 import numpy as np
 import matplotlib.pyplot as plt
 
-rows = 2**5
-cols = 2**5
+rows = 4
+cols = 4
 
 length = 1.0
 width = 1.0
@@ -20,12 +20,13 @@ alpha = 1e-4
 material = 1.0
 F = 0.0
 rho = 1.0
+initial_b = 50
 
 tub = Bathtub([rows, cols], [length,width], intervals, duration, temperature,
 alpha, material)
 
 heat = Convector(tub)
-vfield = FluidField(tub, F, rho, initial_temp)
+vfield = FluidField(tub, F, rho, initial_temp, 50)
 
 heat.set_vfield(vfield)
 vfield.set_conv(heat)

### 2016-02-01 article/nontech.tex
pushing paper

--- 2016-02-01 article/main.tex
@@
 \begin{abstract}
-    This is a test.
+	Ever wonder what's the how to keep your warm bath at the right temperature while helping the environment?
+This paper introduces and analyzes two-dimensional heat convection-diffusion through the Navier-Stokes formulation of fluid-flow and the classical heat equation.
+Our mission is to determine the optimal amount of water necessary to maintain the perfect bathtub temperature.
+BLAH BLAH BLAH
 \end{abstract}
@@
 \section{Introduction}
+
+The basis of this paper is to develop a model that permits a person to maintain their preferred temperature of the bathtub water while minimizing water consumption.
 

### 2016-02-01 article/nontech.tex
pushing nontech

--- 2016-01-31 article/main.tex
@@
 \bibliography{main.bib}
-\title{Ethical Academic Software Practices: the Case for Behavior-Driven
-Development}
-\author{David Kraemer}
-\date{November 24, 2015}
-\shorttitle{Behavior-Driven Development in Academia}
-\affiliation{Grinnell College}
-\leftheader{Kraemer}
-\doublespacing
+
+\usepackage[margin=1in]{geometry}
+
+\usepackage{amsmath, amssymb, amsthm}
+
+% Custom macros
+\newcommand{\la}{\overleftarrow}
+\newcommand{\ra}{\overrightarrow}
+\newcommand{\ca}{\overleftrightarrow}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\abs}[1]{\left|#1\right|}
+\DeclareMathOperator*{\argmin}{\mathrm{arg\,min}}
+
+\title{The Perfect Bathtub Experience}
+\date{February 1, 2016}
 
@@
 
-       \printbibliography
+    Ever wonder what's the how to keep your warm bath at the right temperature?
+We have good news for you!
+We have discovered an optimal strategy that permits you to maintain the perfect bathtub temperature.
+We'll begin our discussion of this perfect strategy with how exactly water in the bathtub maintains its warmth.
+
+	Unlike most substances, water is capable of retaining heat for extended periods of time.
+When a substance heats up, the tiny molecules that compose the substance vibrate more quickly.
+The vibrating of the external substances molecules is what we classify as temperature.
+The higher the temperature, the warmer the feel of the substance.
+
+	How does that relate to us humans exactly?
+Substance molecules interact with one another via electromagnetic forces at a very minute distances.
+When a substance meets our skin, the tiny molecules push against with our nerve cells using these electromagnetic forces.
+Subsequently, our nerves respond with feelings of hot, cold, and everything in-between depending on how quickly the substance's molecules are vibrating.
+
+	When vibrations in molecules become excessive, the bonds that hold these molecules together will break, releasing or absorbing heat.
+When a hydrogen bonds to another element, we call this a hydrogen bond; a hydrogen bond, when broken, is an instance where heat is absorbed.
+Water molecules is made up of two hydrogen bonds.
+When water heats up, the surrounding heat is absorbed to account for the breaking hydrogen bonds.
+Consequently, water is able to keep absorb large quantities of heat.
+
+	Now going back to your bathtub, suppose you start you come home from a long day at work, eager to bathe and unwind. You start to fill your bathtub with warm water from its single faucet, and
 

### 2016-02-01 article/main.tex
Look, plots!

@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{amsart}
 
@@
 \usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\usepackage{fancyhdr}
+\usepackage{lastpage}
+\pagestyle{fancy}
+\renewcommand{\headrulewidth}{0.0pt}
+
+\lhead{Team \# 54040}
+\rhead{Page \thepage\ of \pageref{LastPage}}
+\cfoot{}
 
@@
 
+\thispagestyle{fancy}
+\tableofcontents
+
 \begin{abstract}
-    This is a test.
+    Ever wonder what's the how to keep your warm bath at the right temperature
+    while helping the environment? This paper introduces and analyzes
+    two-dimensional heat convection-diffusion through the Navier-Stokes
+    formulation of fluid-flow and the classical heat equation. Our mission is to
+    determine the optimal amount of water necessary to maintain the perfect
+    bathtub temperature. BLAH BLAH BLAH
 \end{abstract}
@@
 Modifying the notation employed by Ames \cite{ames}, we establish the
-following nomenclature for the numerical operations in the model:
+following nomenclature for the numerical operations in the model (the use of $T$
+is without loss of generality and can be substituted for $v$ and $p$ as well):
 
@@
 
-For
+The estimation of partial derivatives using the above techniques result in
+different rates of convergence as the numerical increment decreases. In
+particular, we have
+\begin{equation}
+    \frac{\partial T_{i,j}^n}{\partial x} = \frac{\ra{\Delta_j}T_{i,j}^n}{\Delta
+    x}+ O(\Delta x),
+    \label{eq:\theequation}
+\end{equation}
+(while we use differentiation along the horizontal axis, the
+convergence is without loss of generality of axis), and we similarly have
+\begin{equation}
+    \frac{\partial T_{i,j}^n}{\partial x} = \frac{\la{\Delta_j}T_{i,j}^n}{\Delta
+    x} + O(\Delta x),
+    \label{eq:\theequation}
+\end{equation}
+while for central differencing, we have
+\begin{equation}
+     \frac{\partial T_{i,j}^n}{\partial x} = \frac{\ca{\Delta_j}T_{i,j}^n}{\Delta
+    x} + O((\Delta x)^2).
+    \label{eq:\theequation}
+\end{equation}
+Indeed, as $\Delta x \to 0$ we see that central differencing has a quadratic
+rate of convergence, while forward and backward differencing are linear. For
+this advantage we employ central differencing in computing spatial derivatives.
+However, as the time evolution is simulated on the fly, we cannot have access to
+$T_{i,j}^{n+1}$ when computing $T_{i,j}^n$. We consequently use backward
+differencing to estimate the time derivative.
+
+The approximated Navier-Stokes equations now read
+\begin{align}
+    \frac{\ca{\Delta_{j}}(v_x)_{i,j}^n}{\Delta x} +
+    \frac{\ca{\Delta_{i}}(v_y)_{i,j}^n}{\Delta y} &= 0 \\
+    \frac{\la{\Delta_n}v^{n}_{i,j}}{\Delta t} + (v_x)_{i,j}^{n}
+    \frac{\ca{\Delta_{j}}(v_x)_{i,j}^n}{\Delta x} + (v_y)_{i,j}^n
+    \frac{\ca{\Delta_{i}}(v_y)_{i,j}^n}{\Delta y} &=
+    -\frac{1}{\rho} \left(  \frac{\ca{\Delta_j}p_{i,j}^n}{\Delta
+    x}+\frac{\ca{\Delta_i}p_{i,j}^n}{\Delta y}  \right) + \alpha
+    \left(\frac{\ca{\Delta_{j}}^2(v_x)_{i,j}^n}{(\Delta x)^2} + 
+    \frac{\ca{\Delta_{i}}^2(v_y)_{i,j}^n}{(\Delta y)^2}
+    \right).
+\end{align}
+The Poisson equation is 
+\begin{equation}
+    \frac{\ca{\Delta_{j}}^2p_{i,j}^n}{(\Delta x)^2} + 
+    \frac{\ca{\Delta_{i}}^2p_{i,j}^n}{(\Delta y)^2}
+    = b.
+    \label{eq:\theequation}
+\end{equation}
+Finally, heat convection-diffusion is given by
+\begin{equation}
+    \frac{\la{\Delta_n}T_{i,j}^n}{\Delta t} - \alpha \frac{\ca{\Delta_{j}}^2T_{i,j}^n}{(\Delta x)^2} + 
+    \frac{\ca{\Delta_{i}}^2T_{i,j}^n}{(\Delta y)^2} + (v_x)_{i,j}^n
+    \frac{\ca{\Delta_{j}}T_{i,j}^n}{\Delta x} + (v_y)_{i,j}^n
+    \frac{\ca{\Delta_{i}}T_{i,j}^n}{\Delta y} = 0
+    \label{eq:\theequation}
+\end{equation}
+
+The algorithmic approach we take is as follows. Using the numerical formulas
+given above, isolate the time derivative and set its value to the other side of
+the equation. In the case of temperature, for example, we then update its value
+with
+\begin{equation}
+    T_{i,j}^{n+1} \leftarrow T_{i,j}^{n} + \Delta t \cdot \frac{\partial
+        T_{i,j}^n}{\partial t}.
+    \label{eq:\theequation}
+\end{equation}
+This pattern is used throughout the computer implementation of these models. The
+remaining question is the stability of these results. In fact, as we shall
+discuss in Section 4, these equations can be highly unstable, especially with a
+naive assignment of parameter values.
 
@@
 \begin{equation}
-    \argmin_{c} V(t_{\mathrm{total}}) \quad \text{such that} \quad \int_{0}^{t_{\mathrm{total}}}
-    f_{\mathrm{cont}}(t) \ dt < \gamma,
+    \argmin_{c} \int_{0}^{t_{\mathrm{total}}} V(t) \ dt \quad \text{such that}
+    \quad \int_{0}^{t_{\mathrm{total}}} f_{\mathrm{cont}}(t) \ dt < \gamma,
     \label{eq:\theequation}
@@
 \begin{equation}
-    \argmin_{c} V^{t_{\mathrm{total}}} \quad \text{such that} \quad
+    \argmin_{c} \sum_{t=0}^{t_{\mathrm{total}}}V^{t_{\mathrm{total}}} \quad \text{such that} \quad
     \sum_{t=0}^{t_{\mathrm{total}}} f_{\mathrm{disc}}(t) < \gamma.
@@
 
+The minimization problem posed here captures the major features of the bathtub
+optimizer problem. In our problem, the bather need not frequently calibrate the
+settings of the bathtub; rather, the bathtub ``policy'' reduces to an initial
+choice of $c$. Moreover, the underlying objective is not to get an even temperature
+distribution (as the bather may simply leave the faucet on arbitrarily long to
+achieve this), but to conserve as much water as possible. The temperature
+distribution problem, then, must be seen within the framework of water
+conservation first and not vice versa. On the other hand, the best volume
+minimization policy is $c=0$, so the bounded temperature total variation
+constraint incorporates the desired $c > 0$ aspects of the problem. Finally,
+from both a numerical perspective and a feasibility perspective, demanding
+complete temperature uniformity, $\gamma = 0$, is impossible. Instead, $\gamma$
+represents the degree of tolerance to which the bather can expect a range of
+temperatures in the bathtub.
+
 \section{Empirical results}
 
-\section{Analysis}
+Our work is highly preliminary and requires more study in order to better
+calibrate our models and properly run experiments. However, we simulated a
+number of variously parametrized situations and can report on the model as a
+proof of concept.
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{../plots/diffusion-01.png}
+
+Figure 1: The heat diffusion process in the case of a stationary fluid and
+constant faucet tap. The mesh
+dimensions are $50 \times 50$, $\alpha = 10^{-3}$, $T_{\mathrm{tub}} = 10$, and
+$T_{\mathrm{faucet}} = 30$.
+\end{center}
+
+For example, the above figure shows a heat-diffusion process on a stationary
+fluid. The white ellipsoid in the left side of the image represents temperature
+emanating from the faucet source. Since the faucet water temperature is greater
+than the rest of the bathtub water, we observe temperature diffusion across the
+bathtub over time.
+
+The same configuration yields a decreasing total variation of temperature as a function
+of time, which corroborates with the intuition that heat diffusing from a source
+increases the uniformity of the bathtub heat.
+
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{../plots/tv-01.png}
+
+    Figure 2: Temperature total variation over time in the case of a stationary
+    fluid, with the same parameters as in Figure 1. The monotonicity of the TV
+    function is in line with basic intution.
+\end{center}
+
+We can also examine the case in which the faucet water is turned on only for the
+initial instant. Our proposed optimization model omits this possibility since it
+requires a fixed water flux from the faucet. However, when we formulated the
+model we relied on the intuitive justification that the overall temperature
+would diverge from the faucet temperature. We simulate the heat diffusion in a
+stationary fluid for which the ``faucet'' turns off immediately after the outset
+of the simulation.
+
+\begin{center}
+    \includegraphics[width=0.8\textwidth]{../plots/diffusion-02.png}
+
+    Figure 3: The heat diffusion process in the case of a stationary fluid and
+    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
+    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$.
+\end{center}
+
+We see the overall temperature level decreases rapidly after the first time
+interval, but the uniformity increases.  However, as we modeled total variation
+as deviation from the faucet temperature, we see that the total variation
+receives a higher penalty than before.
+
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{../plots/tv-02.png}
+
+    Figure 4: Temperature total variation over time in the case of a stationary
+    fluid, with the same parameters as in Figure 3. The monotonicity of the TV
+    function is in line with basic intution.
+\end{center}
+The fact that the total variation performs so poorly in this case has
+implications for the policy problem, which we will discuss in the next section.
+
+Generalizing beyond stationary fluids reveals a number of critical issues of the
+numerical techniques employed in this study. In stationary fluid, the
+Navier-Stokes and Poisson equations are not in play; however, by relaxing the
+stationarity constraint, we observe the effects of the numerical instability of
+our approximations to these equtaions. We simulate the case described in Figure
+1 but relax the stationarity constraint.
+
+\begin{center}
+    \includegraphics[width=0.8\textwidth]{../plots/diffusion-03.png}
+
+    Figure 5: The heat diffusion process in the case of a moving fluid and
+    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
+    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
+    parameter controlling the fluid motion is set $b = 5$.
+\end{center}
+
+By comparing Figure 5 with Figure 1, we see that adding the convection process
+into the model actually improves the spread of the faucet temperature. Since
+more of the bathtub area is white in the images, we have more of the surface
+area heated by the temperature water.
+
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{../plots/tv-03.png}
+
+    Figure 6: Temperature total variation (with respect to $T_{\mathrm{faucet}}$
+    and with respect to the mean bathtub temperature over time in the case of a
+    nonstationary fluid, with the same parameters as in Figure 5. The TV
+    functions are considerably less well behaved, but notably the TV with
+    respect to $T_{\mathrm{faucet}}$ decreases to a lower level than the same TV
+    in Figure 2.
+\end{center}
+
+\begin{center}
+    \includegraphics[width=0.8\textwidth]{../plots/diffusion-04.png}
+
+    Figure 7: The heat diffusion process in the case of a moving fluid and
+    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
+    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
+    parameter controlling the fluid motion is set $b = 8$. The numerical
+    instability of the simulation causes the complete whitewashing by the final
+    frame.
+\end{center}
+
+By comparing Figure 5 with Figure 1, we see that adding the convection process
+into the model actually improves the spread of the faucet temperature. Since
+more of the bathtub area is white in the images, we have more of the surface
+area heated by the temperature water.
+
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{../plots/tv-04.png}
+
+    Figure 8: Temperature total variation (with respect to $T_{\mathrm{faucet}}$
+    and with respect to the mean bathtub temperature over time in the case of a
+    nonstationary fluid, with the same parameters as in Figure 5. The TV
+    functions are considerably less well behaved, but notably the TV with
+    respect to $T_{\mathrm{faucet}}$ decreases to a lower level than the same TV
+    in Figure 2.
+\end{center}
+
+The numerical instability persists even when the faucet is turned off, as in
+Figure 3.
 
@@
 
-\nocite{air}
+As we showed in the previous section, our current numerical implementation of
+the Navier-Stokes equations are highly sensitive to the initial conditions of
+the model. Though a careful calibration of the deep parameters (e.g. $\rho$,
+$\alpha$, $\beta$, etc.) and mesh granularity might produce more stable results,
+we doubt that this would be sufficient. Fundamentally, forward Euler
+approximations of the solutions to differential equations encourage volatility 
+by accumulating the relatively small errors from the individual step
+calculations into catastrophically unstable general results. To prevent this
+kind of instability requires a re-examination of the numerical approach to
+approximating these PDEs.
+
+Perhaps somewhat surprising, then, is the fact that diffusion alone seems to
+abstain from these stability problems. Indeed, if numerical differentiation is
+the problem, then diffusion, which computes the Laplacian, should produce even
+greater error. However, due to the simplicity of the stability conditions for
+diffusion (for example, see Barba's discussion \cite{12-steps}), the checks on
+stability can be readily accounted for and poor configuration choices can simply
+be avoided. This was the approach of the study. From a cursory glance at the
+Navier-Stokes and Poisson equations we understand that the stability conditions
+are not necessarily so simple, but incorporating them should help improve the
+reliability of the model.
+
+That maintaining an active source (in the case of the bathtub narrative, a
+running faucet) reduces the total variation of the temperature in the bathtub
+supports our formulation of the optimization problem and also indicates suitable
+choices for $\gamma$. If the optimization problem requires a bound
+
+\nocite{*}
 

### 2016-02-01 article/nontech.tex

@@
-\documentclass[12pt]{article}
+\documentclass[10pt]{article}
 
@@
 
-	Now going back to your bathtub, suppose you start you come home from a long day at work, eager to bathe and unwind. You start to fill your bathtub with warm water from its single faucet, and
+	Now going back to your bathtub, suppose you come home from a long day at work, eager to bathe and unwind.
+You start to fill your bathtub with warm water from its single faucet.
+Unfortunately, you do not have a fancy tub with secondary heating systems like circulating jets, so the only way to warm your bathtub is through the faucet.
+Then you step in to the bathtub to clean and relax.
+After some time later, you notice the water in the tub is cooler than what you would like.
+How do you fix this?
+
+	Using the faucet, turn on the water to slightly warmer than you would prefer.
+Now sure water is great heat retainer, but how about water entering the tub?
+How can we maintain the specific temperature of the bathtub water?
+Water is a liquid, so it takes the shape of its container.
+When water enters the bathtub, it will spread uniformly throughout the bathtub floor and accumulate upon itself due to gravity pulling the water molecules downward.
+Any substance does not like to stay warm however.
+Warmer temperatures like to diffuse to lower temperatures to promote a uniform temperature throughout.
+As such, the water in the bathtub will lose heat to the air above it and the surface of the bathtub.
+Because the faucet is positioned at one end of the bathtub and your body takes up solid space pushing water to the fringes of the bathtub, it's impossible to have perfectly uniform water temperature in your bath.
+However, the solution to this problem is to maintain constant water flow in the bathtub, even at a low pressure - this way the warm water will continually cycle into your bathtub and out the drain when it reaches a certain height.
+The loss of heat to the surrounding environment is taken into account for by the slightly warmer water temperature from the faucet.
+
+	For those of you whom like to include bubble bath in your bathtub, you're in luck: bubble bath aids water's heat retention abilities by providing more outlets for water to push its heat towards.
+In the short term, you will have less issues maintaining your warm bubble bath for a longer period of time.
+In the long term however, you will need to resort to trickling water into the bathtub to maintain heat just like if you were not using bubble bath at all.
+
+	And there it is folks! The perfect bath secrets exposed.
 

### 2016-02-01 article/main.tex
Closer to the final draft

@@
 \usepackage{amsmath, amssymb, amsthm}
+\usepackage{ragged2e}
 
@@
 \begin{abstract}
-    Ever wonder what's the how to keep your warm bath at the right temperature
-    while helping the environment? This paper introduces and analyzes
-    two-dimensional heat convection-diffusion through the Navier-Stokes
-    formulation of fluid-flow and the classical heat equation. Our mission is to
-    determine the optimal amount of water necessary to maintain the perfect
-    bathtub temperature. BLAH BLAH BLAH
 \end{abstract}
@@
 
+\justify
+\footnotesize{
 Figure 1: The heat diffusion process in the case of a stationary fluid and
@@
 dimensions are $50 \times 50$, $\alpha = 10^{-3}$, $T_{\mathrm{tub}} = 10$, and
-$T_{\mathrm{faucet}} = 30$.
+$T_{\mathrm{faucet}} = 30$.}
 \end{center}
@@
 
+    \justify
+    \footnotesize{
     Figure 2: Temperature total variation over time in the case of a stationary
     fluid, with the same parameters as in Figure 1. The monotonicity of the TV
-    function is in line with basic intution.
+function is in line with basic intution.}
 \end{center}
@@
 
+    \justify
+    \footnotesize{
     Figure 3: The heat diffusion process in the case of a stationary fluid and
     temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
-    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$.
+    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$.}
 \end{center}
@@
 
+    \justify
+    \footnotesize{
     Figure 4: Temperature total variation over time in the case of a stationary
     fluid, with the same parameters as in Figure 3. The monotonicity of the TV
-    function is in line with basic intution.
+function is in line with basic intution.}
 \end{center}
@@
 Generalizing beyond stationary fluids reveals a number of critical issues of the
-numerical techniques employed in this study. In stationary fluid, the
+numerical techniques employed in this study, but also provides useful
+information regarding the underlying problem. In stationary fluid, the
 Navier-Stokes and Poisson equations are not in play; however, by relaxing the
-stationarity constraint, we observe the effects of the numerical instability of
-our approximations to these equtaions. We simulate the case described in Figure
-1 but relax the stationarity constraint.
+stationarity constraint, we observe the effects fluid flow on the diffusivity of
+heat. We simulate the case described in Figure 1 but relax the stationarity constraint.
 
@@
 
+    \justify
+    \footnotesize{
     Figure 5: The heat diffusion process in the case of a moving fluid and
-    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
+    permanent faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
     10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
-    parameter controlling the fluid motion is set $b = 5$.
+parameter controlling the fluid motion is set $b = 5$.}
 \end{center}
@@
 more of the bathtub area is white in the images, we have more of the surface
-area heated by the temperature water.
+area heated by the temperature water. This phenomenon is confirmed by measuring
+the total variation of the bathtub water over time.
 
@@
 
+    \justify
+    \footnotesize{
     Figure 6: Temperature total variation (with respect to $T_{\mathrm{faucet}}$
@@
     respect to $T_{\mathrm{faucet}}$ decreases to a lower level than the same TV
-    in Figure 2.
+in Figure 2.}
 \end{center}
+
+There are three interesting phenomena present in this result. First, we see that
+the evolution of the total variation over time is less well-behaved than before.
+We also note that the total variation with respect to the mean bathtub
+temperature grows almost linearly with time and exhibits much less concavity
+than Figure 2. Finally, the total variation with respect to
+$T_{\mathrm{faucet}}$ reaches a lower threshold than the total variation in the
+diffusion case only in Figure 2.
+
+The choice of $b=5$ is essntially arbitrary; however the behavior of the fluid
+with respect to different choices is highly volatile. In fact, modest changes to
+the value for $b$ have drastic implications for the numerical stability of the
+fluid flow, and consequently the temperature. We see this phenomenon in Figures
+7 and 8.
 
@@
 
+    \justify
+    \footnotesize{
     Figure 7: The heat diffusion process in the case of a moving fluid and
-    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
+    permanent faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
     10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
@@
     instability of the simulation causes the complete whitewashing by the final
-    frame.
+frame.}
 \end{center}
 
-By comparing Figure 5 with Figure 1, we see that adding the convection process
-into the model actually improves the spread of the faucet temperature. Since
-more of the bathtub area is white in the images, we have more of the surface
-area heated by the temperature water.
+The evolution of frames in Figure 7 represents an explosion in the numerical
+values associated with the temperatures. The black-white ridge in the bottom
+right corner of the third frame exhibits the typical instability phenomenon we
+observed in the simulations. Emanating from near the faucet source, this
+phenomenon appears to push out towards the boundary of the frame until the
+entire frame is whitewashed. We can also see this last-minute explosion by
+measuring the total variation.
 
@@
 
+    \justify
+    \footnotesize{
     Figure 8: Temperature total variation (with respect to $T_{\mathrm{faucet}}$
@@
     respect to $T_{\mathrm{faucet}}$ decreases to a lower level than the same TV
-    in Figure 2.
+in Figure 2.}
 \end{center}
 
-The numerical instability persists even when the faucet is turned off, as in
-Figure 3.
+The presence of a constant heat and flow source in the faucet might suggest that
+the numerical instability associated with the parametrization of $b$ relates
+also to the source. We see that this is not the case. The numerical instability
+persists even when the faucet is turned off, as in Figure 3.
+
+\begin{center}
+    \includegraphics[width=0.8\textwidth]{../plots/diffusion-05.png}
+
+    \justify
+    \footnotesize{Figure 9: The heat diffusion process in the case of a moving fluid and
+    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
+    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
+    parameter controlling the fluid motion is set $b = 8$. The numerical
+    instability of the simulation causes the complete whitewashing by the final
+frame.}
+\end{center}
+
+Interestingly, the second frame seems to show numerical instability towards
+underflow, but by the third frame we observe near complete whitewashing of the
+same characterization as Figure 7. We also see the black-white ridge in the
+bottom right corner of the third frame, again in a similar fashion to Figure 7.
+
+More surprisingly is the behavior of the temperature total variation, as we see
+below in Figure 10.
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{../plots/tv-05.png}
+
+    \justify
+    \footnotesize{
+        Figure 10: Temperature total variation (with respect to
+        $T_{\mathrm{faucet}}$ and with respect to the mean bathtub temperature
+        over time in the case of a nonstationary fluid, with the same parameters
+        as in Figure 9. The TV functions are very poorly behaved and exhibit no
+        similar characteristics to the previous configurations of the
+        simulation.}
+\end{center}
+We have no intuition or explanation for the behavior of these total variation
+functions. We suspect that this is almost entirely due to numerical artifacts in
+the simulation but cannot speak with any authority to why the hump shape appears
+in the plots. We do note, however, that the hump appears to correspond to the
+second frame of Figure 9, in which we observe a very dark region with low
+temperature.
 
@@
 the model. Though a careful calibration of the deep parameters (e.g. $\rho$,
-$\alpha$, $\beta$, etc.) and mesh granularity might produce more stable results,
+$\alpha$, $b$, etc.) and mesh granularity might produce more stable results,
 we doubt that this would be sufficient. Fundamentally, forward Euler
@@
 supports our formulation of the optimization problem and also indicates suitable
-choices for $\gamma$. If the optimization problem requires a bound
+choices for $\gamma$. Since including nonstationarity reduces the total
+variation of the temperature the farthest, we can suggest to the avid bather
+that keeping the water moving in the bathtub likely keeps the bathtub
+temperature more evenly distributed than letting the water approach
+stationarity.
+
+Further investigation should attempt to mitigate the detrimental effects of
+unchecked numerical instability. The mesh approach to the numerical
+approximation of PDE solutions can be optimized \cite{betounes, 12-steps} to
+minimize the accumulation of error. Solving our proposed optimization problem
+requires additional study, too. Ultimately, our avid bather needs a policy to
+maximize her utility, so specifying the ideal velocity $c$ remains the future
+priority.
 

### 2016-02-01 article/main.tex
merging changes to main.tex

--- 2016-02-01 article/main.tex
@@
-\documentclass[12pt]{amsart}
+\documentclass[12pt]{article}
 
@@
 \usepackage{graphicx}
-\usepackage{fancyhdr}
-\usepackage{lastpage}
-\pagestyle{fancy}
-\renewcommand{\headrulewidth}{0.0pt}
-
-\lhead{Team \# 54040}
-\rhead{Page \thepage\ of \pageref{LastPage}}
-\cfoot{}
 
@@
 \maketitle
-
-\thispagestyle{fancy}
 \tableofcontents
@@
 \begin{abstract}
-    Ever wonder what's the how to keep your warm bath at the right temperature
-    while helping the environment? This paper introduces and analyzes
-    two-dimensional heat convection-diffusion through the Navier-Stokes
-    formulation of fluid-flow and the classical heat equation. Our mission is to
-    determine the optimal amount of water necessary to maintain the perfect
-    bathtub temperature. BLAH BLAH BLAH
+
 \end{abstract}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../plots/diffusion-01.png}
+\includegraphics[width=0.8\textwidth]{../plots/diffusion.png}
 
@@
 
-The same configuration yields a decreasing total variation of temperature as a function
+The same setup yields a decreasing total variation of temperature as a function
 of time, which corroborates with the intuition that heat diffusing from a source
@@
 We can also examine the case in which the faucet water is turned on only for the
-initial instant. Our proposed optimization model omits this possibility since it
-requires a fixed water flux from the faucet. However, when we formulated the
-model we relied on the intuitive justification that the overall temperature
-would diverge from the faucet temperature. We simulate the heat diffusion in a
-stationary fluid for which the ``faucet'' turns off immediately after the outset
-of the simulation.
+initial instant. Here, as we expect, the overall temperature level decreases
+rapidly after the first time interval, but the uniformity increases.
 
@@
 
-We see the overall temperature level decreases rapidly after the first time
-interval, but the uniformity increases.  However, as we modeled total variation
-as deviation from the faucet temperature, we see that the total variation
-receives a higher penalty than before.
+However, as we modeled total variation as deviation from the faucet temperature,
+we see that the total variation receives a higher penalty than before.
 
@@
 \end{center}
+
 The fact that the total variation performs so poorly in this case has
 implications for the policy problem, which we will discuss in the next section.
-
 Generalizing beyond stationary fluids reveals a number of critical issues of the
-numerical techniques employed in this study. In stationary fluid, the
-Navier-Stokes and Poisson equations are not in play; however, by relaxing the
-stationarity constraint, we observe the effects of the numerical instability of
-our approximations to these equtaions. We simulate the case described in Figure
-1 but relax the stationarity constraint.
-
-\begin{center}
-    \includegraphics[width=0.8\textwidth]{../plots/diffusion-03.png}
-
-    Figure 5: The heat diffusion process in the case of a moving fluid and
-    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
-    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
-    parameter controlling the fluid motion is set $b = 5$.
-\end{center}
-
-By comparing Figure 5 with Figure 1, we see that adding the convection process
-into the model actually improves the spread of the faucet temperature. Since
-more of the bathtub area is white in the images, we have more of the surface
-area heated by the temperature water.
-
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{../plots/tv-03.png}
-
-    Figure 6: Temperature total variation (with respect to $T_{\mathrm{faucet}}$
-    and with respect to the mean bathtub temperature over time in the case of a
-    nonstationary fluid, with the same parameters as in Figure 5. The TV
-    functions are considerably less well behaved, but notably the TV with
-    respect to $T_{\mathrm{faucet}}$ decreases to a lower level than the same TV
-    in Figure 2.
-\end{center}
-
-\begin{center}
-    \includegraphics[width=0.8\textwidth]{../plots/diffusion-04.png}
-
-    Figure 7: The heat diffusion process in the case of a moving fluid and
-    temporary faucet tap. The mesh dimensions are $50 \times 50$, $\alpha =
-    10^{-3}$, $T_{\mathrm{tub}} = 10$, and $T_{\mathrm{faucet}} = 30$. The
-    parameter controlling the fluid motion is set $b = 8$. The numerical
-    instability of the simulation causes the complete whitewashing by the final
-    frame.
-\end{center}
-
-By comparing Figure 5 with Figure 1, we see that adding the convection process
-into the model actually improves the spread of the faucet temperature. Since
-more of the bathtub area is white in the images, we have more of the surface
-area heated by the temperature water.
-
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{../plots/tv-04.png}
-
-    Figure 8: Temperature total variation (with respect to $T_{\mathrm{faucet}}$
-    and with respect to the mean bathtub temperature over time in the case of a
-    nonstationary fluid, with the same parameters as in Figure 5. The TV
-    functions are considerably less well behaved, but notably the TV with
-    respect to $T_{\mathrm{faucet}}$ decreases to a lower level than the same TV
-    in Figure 2.
-\end{center}
-
-The numerical instability persists even when the faucet is turned off, as in
-Figure 3.
+numerical techniques employed in this study.
 
 \section{Discussion}
-
-As we showed in the previous section, our current numerical implementation of
-the Navier-Stokes equations are highly sensitive to the initial conditions of
-the model. Though a careful calibration of the deep parameters (e.g. $\rho$,
-$\alpha$, $\beta$, etc.) and mesh granularity might produce more stable results,
-we doubt that this would be sufficient. Fundamentally, forward Euler
-approximations of the solutions to differential equations encourage volatility 
-by accumulating the relatively small errors from the individual step
-calculations into catastrophically unstable general results. To prevent this
-kind of instability requires a re-examination of the numerical approach to
-approximating these PDEs.
-
-Perhaps somewhat surprising, then, is the fact that diffusion alone seems to
-abstain from these stability problems. Indeed, if numerical differentiation is
-the problem, then diffusion, which computes the Laplacian, should produce even
-greater error. However, due to the simplicity of the stability conditions for
-diffusion (for example, see Barba's discussion \cite{12-steps}), the checks on
-stability can be readily accounted for and poor configuration choices can simply
-be avoided. This was the approach of the study. From a cursory glance at the
-Navier-Stokes and Poisson equations we understand that the stability conditions
-are not necessarily so simple, but incorporating them should help improve the
-reliability of the model.
-
-That maintaining an active source (in the case of the bathtub narrative, a
-running faucet) reduces the total variation of the temperature in the bathtub
-supports our formulation of the optimization problem and also indicates suitable
-choices for $\gamma$. If the optimization problem requires a bound
 

### 2016-02-01 article/nontech.tex
more nontech

@@
 
-	For those of you whom like to include bubble bath in your bathtub, you're in luck: bubble bath aids water's heat retention abilities by providing more outlets for water to push its heat towards.
-In the short term, you will have less issues maintaining your warm bubble bath for a longer period of time.
-In the long term however, you will need to resort to trickling water into the bathtub to maintain heat just like if you were not using bubble bath at all.
+	Another helpful tactic to maintaining your bathtub temperature is to keep the water constantly in motion.
+You can help this process by moving around in the bathtub to move the warm water from the faucet to the outer reaches of the bathtub not near the faucet.
+This tactic helps because warm water from the faucet diffuses its heat to the surrounding cooler water molecules.
+When colder water molecules are surrounded by warmer water molecules, the bathtub water will heat up faster.
 
-	And there it is folks! The perfect bath secrets exposed.
+	And there it is folks!
+The perfect bath secrets exposed.
+To reiterate, the optimal strategy is to maintain a constant input of warm water from the faucet and to assist the warm water flow from to the various sides of the bathtub.
 

### 2016-02-01 article/main.tex
Closer to the final draft

--- 2016-02-01 article/main.tex
@@
 
-\title{Numerical simulation of two-dimensional heat convection-diffusion with
-ellipsoid geometries}
+\title{Keeping it even: maintaining evenly distributed temperatures within a
+two-dimensional bathtub}
 
@@
 
-The basis of this paper is to develop a model that permits a person to maintain their preferred temperature of the bathtub water while minimizing water consumption.
+The avid bather faces the constant struggle in balancing her ability to relax in
+the bathtub and in keeping an evenly distributed water temperature within the
+tub. For such a bather a quality bath is a necessity. Necessity, the mother of
+invention, requires that quality be sought after and maximized---the bather
+should need to worry as little as possible about the quality of the temperature
+distribution in the tub. To help our bather, we seek to give a precise
+determination of quality and pose a question in whose answer provides the best
+such quality. Yet living in a world of scarce resources demands attention
+towards the cost of our decisions. Our underlying quest for quality needs
+temperament from reality, and we shall formulate the problem as a trade-off
+between these competing camps.
+
+In this work, we begin by developing a model for the evolution of heat in a
+bathtub. Heat travels through a fluid by two means: diffusion and convection.
+The diffusion process refers to the natural spread of heat from high-temperature
+peaks to low-temperature valleys. This process is fundamentally spatial and
+occurs even in the context of a stationary fluid. The convection process, by
+contrast, refers to the spread of heat subject to a moving fluid. Heat can flow
+with a fluid to spread along the direction the fluid travels; this process helps
+to explain the behavior of ocean conveyor belts and hurricanes. In order to
+optimize the distribution of heat, we need to understand how heat evolves. This
+will be the primary scope of our paper.
+
+Our work proceeds as follow. Section 2 describes the high-level view of the
+computational model for simulating the evolution of heat in a bathtub in the
+context of both a stationary and moving fluid. It also outlines the numerical
+methods we will use in order to approximate the underlying diffusion and
+convection processes. We also propose, but do not solve, the bather's
+optimization problem. Section 3 provides the results of our initial
 
@@
 
+\subsection{Heat diffusion in a stationary fluid}
+
 \begin{center}
@@
 implications for the policy problem, which we will discuss in the next section.
+
+\subsection{Nonstationarity and numerical stability}
 

### 2016-02-01 article/abstract.tex
adding abstract

\documentclass[10pt]{article}

\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

\usepackage{csquotes}
\usepackage[style=numeric,
    citestyle=numeric,
    backend=biber,
    natbib=true,
url=true]{biblatex}

\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{microtype}

\bibliography{main.bib}

\usepackage[margin=1in]{geometry}

\usepackage{amsmath, amssymb, amsthm}

% Custom macros
\newcommand{\la}{\overleftarrow}
\newcommand{\ra}{\overrightarrow}
\newcommand{\ca}{\overleftrightarrow}
\newcommand{\R}{\mathbb{R}}
\newcommand{\abs}[1]{\left|#1\right|}
\DeclareMathOperator*{\argmin}{\mathrm{arg\,min}}

\title{Abstract}

\begin{document}

\maketitle

This paper presents a numerical approach to maintaining an ideal temperature in a bathtub while minimizing water usage. In our approach, we utilize the Navier-Stokes formulation of fluid flow and the classical heat equation to model water constrained to a bathtub-like container. The container acts as a closed-system consisting of the bathtub, the water inside the bathtub, and the faucet. The bathtub water is subjected to environmental conditions such as the bathtub absorbing heat from the water, heat loss due to convection with the air particles immediately above the bathtub, adding warm water from the faucet, and placing an avid bather inside the bathtub.

The model uses two different "policies" to model the water: the case of a stationary fluid, and when fluid is allowed to move throughout the bathtub. Within the stationary fluid situation, our model monitors when the faucet is on for a infinitesimal time and then the faucet is turned on throughout the entire duration. We utilize these environmental conditions to minimize the variance between the ideal bathtub temperature and the temperature some time after the initial setup. This paper pays particular attention to the numerical instability of fluid flows, temperature diffusion, and how our choice of "policy" affects the simulation.
\end{document}

### 2016-02-01 article/main.tex
adding abstract
cover and nontech final

@@
 \begin{abstract}
+This paper presents a numerical approach to maintaining an ideal temperature in a bathtub while minimizing water usage.
+In our approach, we utilize the Navier-Stokes formulation of fluid flow and the classical heat equation to model water constrained to a bathtub-like container.
+The container acts as a closed-system consisting of the bathtub, the water inside the bathtub, and the faucet.
+The bathtub water is subjected to environmental conditions such as the bathtub absorbing heat from the water, heat loss due to convection with the air particles immediately above the bathtub, adding warm water from the faucet, and placing an avid bather inside the bathtub.
+
+The model uses two different "policies" to model the water: the case of a stationary fluid, and when fluid is allowed to move throughout the bathtub.
+Within the stationary fluid situation, our model monitors when the faucet is on for a infinitesimal time and then the faucet is turned on throughout the entire duration.
+We utilize these environmental conditions to minimize the variance between the ideal bathtub temperature and the temperature some time after the initial setup.
+This paper pays particular attention to the numerical instability of fluid flows, temperature diffusion, and how our choice of "policy" affects the simulation.
 \end{abstract}
